### 2022-07-06 Papers/ICCC-2023/sections/design.tex
design

\subsection{Design of C-=-1}

@@

\subsection{Design of the compiler}

\subsubsection{Frontend}

>>>>

CTFE First apporach was created during implementation of the first compiler for the C-=-1 language\cite{grabski2022compilation}.
The need for a new approach to compiler construction arose due to the unusal characteristics of the language, further described in chapter \ref{language-design}.
Chapter \ref{compiler-design} describes the CTFE First approach and how the compiler is structured.

\subsection{Design of C-=-1}
\label{language-design}

C-=-1 was designed as a compiled, low-level, non-garbage-collected programming language, similar to C, C++ or Rust.
What diffirentiates C-=-1 are its two founding principles: all code is executable at compile-time and support rich metaprogramming.
The primary purpose of the language was to research how these ideas influence software written in it \cite{grabski2022compilation}.

@@

\subsection{Design of the compiler}
\label{compiler-design}
\subsubsection{Frontend}
